### 2018-07-30 Sections/state_of_the_art.tex
Fix document structure hierarchy

\section{State-of-the-art} \label{sec:state_of_the_art} \index{State-of-the-art}

@@

\subsection{Quantum teleportation \& entanglement distribution} \index{Quantum state teleportation} \index{Quantum gate teleportation} \index{Entanglement distribution}

Quantum state teleportation has attracted broad experimental interest and been subject to widespread demonstration across many physical architectures, becoming one of the most well investigated protocols in experimental quantum information science. Table.~\ref{tab:state_tomo} summarises some of the notable developments.

@@

\subsection{Entanglement swapping \& quantum repeaters} \index{Entanglement swapping} \index{Quantum repeater networks}

Closely related to entanglement distribution is entanglement swapping (Sec.~\ref{sec:swapping}), where the goal is to entangle two remote parties, each of whom have one half of two distinct Bell pairs. As discussed in Sec.~\ref{sec:ent_ultimate}, entanglement swapping will be of fundamental importance in networks treating entanglement distribution as the most fundamental elementary resource, making it of great importance to quantum networking, allowing the distribution of entanglement between distant parties, who are unable to communicate directly (i.e the entanglement distribution is `mediated').

@@

\subsection{Quantum key distribution} \index{Quantum key distribution (QKD)}\ref{bib:QKD_state_of_art}

With the development of quantum technology, QKD will gradually become more and more practical and economically accessible. Bennett, one of the proposers of the BB84 protocol, first demonstrated the protocol on an optical platform with a distance of 30cm \cite{bib:JC_5_3}. Since then, experiments have developed rapidly from indoors to outdoors, over ever-increasing distances, with commercial QKD units even available as off-the-shelf products. Table.~\ref{tab:QKD_table} summarises some major developments in the field.

@@

\subsection{Entanglement purification} \index{Entanglement purification}

@@

Entanglement purification has been very successful in optical systems. Table.~\ref{tab:ent_pur} lists some of the major developments.

@@

\subsection{State preparation} \index{State preparation}

@@

\subsubsection{Coherent states} \index{Coherent state preparation}

@@

\subsubsection{Single-photon states} \index{Single-photon state preparation}

@@

\subsubsection{Entangled states based on non-linear optics} \index{Non-linear optics}

@@

\subsection{Non-optical systems} \index{Matter qubits}

@@

\subsubsection{Atomic ensembles} \index{Atomic ensembles}

@@

\subsubsection{Single atoms} \index{Single atoms}

@@

\subsubsection{Quantum dots} \index{Quantum dot sources}

@@

\subsubsection{Nitrogen-vacancy centres} \index{Nitrogen-vacancy (NV) centres}

@@

\subsubsection{Superconducting rings} \index{Superconducting rings}

@@

\subsection{Measurement} \index{Measurement}

@@

\subsubsection{Photo-detection} \index{Photo-detection}

@@

\subsubsection{Homodyning} \index{Homodyne detection}

@@

\subsection{Evolution of optical states} \index{Evolution of optical states} \label{sec:LO_evolution}

@@

\subsubsection{Optical waveguides} \index{Optical waveguides}

@@

\subsubsection{Fibre-loops} \index{Time-bin encoding} \index{Fibre-loops}

@@

\subsubsection{Others}

@@

\subsection{Quantum memory} \index{Quantum memory}

Many review articles can give a much more detailed account such as \cite{lvovsky2009optical, simon2010quantum, sangouard2011quantum, bussieres2013prospective, reiserer2015cavity}.

@@

\subsection{Quantum computation}\index{Quantum computing}

@@

\subsubsection{Linear optics}\index{Universal linear optics quantum computation}

\subsubsection{Boson-sampling \& quantum walks}\index{Boson-sampling}\index{Quantum walks}

\subsubsection{Ion traps}\index{Ion traps}

\subsubsection{Superconducting rings}\index{Superconducting rings}

\subsubsection{Nitrogen-vacancy centres}\index{Nitrogen-vacancy (NV) centres}

\subsubsection{Adiabatic quantum computation \& quantum annealing}\index{Adiabatic quantum computation}\index{Quantum annealing}

>>>>

@@

\section{Quantum teleportation \& entanglement distribution} \index{Quantum state teleportation} \index{Quantum gate teleportation} \index{Entanglement distribution}

\dropcap{Q}{uantum} state teleportation has attracted broad experimental interest and been subject to widespread demonstration across many physical architectures, becoming one of the most well investigated protocols in experimental quantum information science. Table.~\ref{tab:state_tomo} summarises some of the notable developments.

@@

\section{Entanglement swapping \& quantum repeaters} \index{Entanglement swapping} \index{Quantum repeater networks}

\dropcap{C}{losely} related to entanglement distribution is entanglement swapping (Sec.~\ref{sec:swapping}), where the goal is to entangle two remote parties, each of whom have one half of two distinct Bell pairs. As discussed in Sec.~\ref{sec:ent_ultimate}, entanglement swapping will be of fundamental importance in networks treating entanglement distribution as the most fundamental elementary resource, making it of great importance to quantum networking, allowing the distribution of entanglement between distant parties, who are unable to communicate directly (i.e the entanglement distribution is `mediated').

@@

\section{Quantum key distribution} \index{Quantum key distribution (QKD)}\ref{bib:QKD_state_of_art}

\dropcap{W}{ith} the development of quantum technology, QKD will gradually become more and more practical and economically accessible. Bennett, one of the proposers of the BB84 protocol, first demonstrated the protocol on an optical platform with a distance of 30cm \cite{bib:JC_5_3}. Since then, experiments have developed rapidly from indoors to outdoors, over ever-increasing distances, with commercial QKD units even available as off-the-shelf products. Table.~\ref{tab:QKD_table} summarises some major developments in the field.

@@

\section{Entanglement purification} \index{Entanglement purification}

@@

\dropcap{E}{ntanglement} purification has been very successful in optical systems. Table.~\ref{tab:ent_pur} lists some of the major developments.

@@

\section{State preparation} \index{State preparation}

@@

\subsection{Coherent states} \index{Coherent state preparation}

@@

\subsection{Single-photon states} \index{Single-photon state preparation}

@@

\subsection{Entangled states based on non-linear optics} \index{Non-linear optics}

@@

\section{Non-optical systems} \index{Matter qubits}

@@

\subsection{Atomic ensembles} \index{Atomic ensembles}

@@

\subsection{Single atoms} \index{Single atoms}

@@

\subsection{Quantum dots} \index{Quantum dot sources}

@@

\subsection{Nitrogen-vacancy centres} \index{Nitrogen-vacancy (NV) centres}

@@

\subsection{Superconducting rings} \index{Superconducting rings}

@@

\section{Measurement} \index{Measurement}

@@

\subsection{Photo-detection} \index{Photo-detection}

@@

\subsection{Homodyning} \index{Homodyne detection}

@@

\section{Evolution of optical states} \index{Evolution of optical states} \label{sec:LO_evolution}

@@

\subsection{Optical waveguides} \index{Optical waveguides}

@@

\subsection{Fibre-loops} \index{Time-bin encoding} \index{Fibre-loops}

@@

\subsection{Others}

@@

\section{Quantum memory} \index{Quantum memory}

\dropcap{M}{any} review articles can give a much more detailed account such as \cite{lvovsky2009optical, simon2010quantum, sangouard2011quantum, bussieres2013prospective, reiserer2015cavity}.

@@

\section{Quantum computation}\index{Quantum computing}

@@

\subsection{Linear optics}\index{Universal linear optics quantum computation}

\subsection{Boson-sampling \& quantum walks}\index{Boson-sampling}\index{Quantum walks}

\subsection{Ion traps}\index{Ion traps}

\subsection{Superconducting rings}\index{Superconducting rings}

\subsection{Nitrogen-vacancy centres}\index{Nitrogen-vacancy (NV) centres}

\subsection{Adiabatic quantum computation \& quantum annealing}\index{Adiabatic quantum computation}\index{Quantum annealing}
